Reanalysis Step 2: Multiple Imputation

### 2025-08-30 reanalysis-2-multiple_imputation.qmd
debug

>>>>

# Save the predictor matrix to CSV for inspection
pred_matrix_df <- as.data.frame(pred_matrix)
pred_matrix_df <- cbind(Variable = rownames(pred_matrix_df), pred_matrix_df)
write.csv(pred_matrix_df, file.path(reanalysis_data_dir, "predictor_matrix.csv"), row.names = FALSE)
log_message(paste0("Saved predictor matrix to: ", file.path(reanalysis_data_dir, "predictor_matrix.csv")))
